Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Change the title
Some words on Castagna.

\title{Contracts for unions and intersections are hard for Nickel}
\author{Teodoro Freund}
\affiliation{
  \institution{Universidad de Buenos Aires}
  \city{Buenos Aires}
  \country{Argentina}
}
\email{tfreund95@gmail.com}

@@

\section{Related work}
\label{sec:related-work}
\info{Including a mention of statically typed systems with union}

>>>>

\title{Union and intersection contracts are hard, actually}
\author{Teodoro Freund}
\affiliation{
  \institution{Universidad de Buenos Aires}
  \city{Buenos Aires}
  \country{Argentina}
}
\email{tfreund95@gmail.com}

@@

\section{(More) Related work}
\label{sec:related-work}
\info{Including a mention of statically typed systems with union}

\subsection{Gradual typing: a new perspective}

Castagna et. al \cite{gradualCastagna} present a gradual type system that
incorporates multiple non-trivial typing constructs, in particular, subtyping,
unions, recursive types, negation types, and a bottom type.
Which can easily encode intersection, difference, and top types.

This system, even if related to the ones we studied, adheres to a different
school of gradual typing, Greenberg would call it the static first
school\cite{practiceTheoryGrad}.
In this line of work, the goal is usually to develop a type system that can
handle a dynamic type to represent the lack of precission on some type.
The main reasons why we consider this work not comparable with what we attempted
to solve are:
\begin{itemize}
  \item Like Williams et al\cite{RootCauseOfBlame}, it doesn't allow
        to use user defined contracts.
  \item Their base calculus needs to have a non-trivial type inference
        algorithm, that makes the development of a programming language
        much more cumbersome. For instance, it defines a set-theoretic
        interpretation of types, and a subtyping relation based on it.
  \item Contracts are completely handled by the execution engine (in the paper,
        the rewriting system), and not added as a library with some basic
        syntactic support.
\end{itemize}
